|

### 2020-07-24 paper.Rmd
Picture to explain projected area better.

>>>>

XXX maybe a better picture is going from a 2D circle to a 1D projection?

```{r, out.width="40%", fig.align = "center"}

xp <- 0.1
n <- 200

x <- seq(-xp, xp,length.out = n)
yp <- sqrt(1-x^2)
ym <- -yp

x_outer1 <- c(seq(1-xp, 1, length.out = n/2))
yp_outer1 <- sqrt(1-x_outer1^2)
ym_outer1 <- -yp_outer1

x_outer2 <- c(seq(-1, -1+xp, length.out = n/2))
yp_outer2 <- sqrt(1-x_outer2^2)
ym_outer2 <- -yp_outer2

ggplot() +
  geom_circle(aes(x0= 0, y0=0, r = 1)) +
  geom_area(aes(x=x, y=yp), fill = "red", alpha = 0.5) +
  geom_area(aes(x=x, y=ym), fill = "red", alpha = 0.5) +
  geom_area(aes(x=x_outer1, y=yp_outer1), fill = "blue", alpha = 0.5) +
  geom_area(aes(x=x_outer1, y=ym_outer1), fill = "blue", alpha = 0.5) +
  geom_area(aes(x=x_outer2, y=yp_outer2), fill = "blue", alpha = 0.5) +
  geom_area(aes(x=x_outer2, y=ym_outer2), fill = "blue", alpha = 0.5) +
  geom_area(aes(x=x_outer1-1+xp, y=yp_outer1), fill = "blue", alpha = 0.5) +
  geom_area(aes(x=x_outer1-1+xp, y=ym_outer1), fill = "blue", alpha = 0.5) +
  geom_area(aes(x=x_outer2+1-xp, y=yp_outer2), fill = "blue", alpha = 0.5) +
  geom_area(aes(x=x_outer2+1-xp, y=ym_outer2), fill = "blue", alpha = 0.5) +
  theme_classic() +
  xlab("x") + ylab("y") +
  coord_fixed()
